Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-02-27 automatica/paper.tex
combined contributions and extensions over cav'17

\addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
In summary, this paper makes the following original contributions.
%
\begin{enumerate}

  % Additions from CAV:
  % continuous time
  % floating point 
\item We automatically generate {\em correct-by-construction} digital
  controllers using an inductive synthesis approach.  Our application of program
  synthesis is non-trivial and addresses challenges specific to control
  systems, such as quantizers and FWL.  %% In particular, we
  %% have found that a two-stage verification engine that continuously refines
  %% the precision of the fixed-point representation of the plant yields a
  %% speed-up of two orders of magnitude over a conventional one-stage
  %% verification engine.
%
  %\item  We compute
  The computed state-feedback controllers 
  guarantee a given safety property alongside stability and safety
  specifications. Existing methods for controller synthesis rely on transfer
  function representations, which are inadequate to prove safety requirements.
%
\item We provide two novel algorithms: the first, na\"ive one, relies on
  an unfolding of the dynamics up to a completeness threshold, while the
  second one is abstraction-based and leverages abstraction refinement and
  acceleration to improve scalability while retaining soundness.  %% A third
  %% algorithm evaluates systems using transfer functions where no state-space
  %% description is given.
  Both approaches provide sound synthesis of
  feedback controllers and consider the various sources of imprecision in
  the implementation of the control algorithm and in the modeling of the
  plant.
%
\item We develop a model for different sources of quantization error and
  their effect on reachability properties.  We give bounds that ensure the
  safety of our controllers in a hybrid continuous-digital domain.
\end{enumerate}

This paper represents an extension of \cite{DBLP:conf/cav/AbateBCCDKKP17} 
in the following directions:
\begin{itemize}
\item While \cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to systems
  modeled in discrete time, in the current paper we present a model for
  soundly evaluating reachability in a combined continuous-discrete time/space.
\item A further limitation of the work in \cite{DBLP:conf/cav/AbateBCCDKKP17}
  is its restriction to fixed-point arithmetic, meaning that fixed-point numbers
  were employed for the representation of both the plant and the controller, as well as for
  the operations performed by each of them.
  Conversely, in the current paper we also make use of floating-point arithmetic
  and compare the two approaches. Additionally, we enhance the implementation with an SMT backend, allowing us to also use reals in order to represent the states of the plant.
\end{itemize}

>>>>

%% \addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
This paper represents an extension of \cite{DBLP:conf/cav/AbateBCCDKKP17}
and makes the following contributions, where the fourth and he fifth denote
extensions over \cite{DBLP:conf/cav/AbateBCCDKKP17}.
%
\begin{enumerate}

  % Additions from CAV:
  % continuous time
  % floating point 
\item We automatically generate {\em correct-by-construction} digital
  controllers using an inductive synthesis approach.  Our application of program
  synthesis is non-trivial and addresses challenges specific to control
  systems, such as quantizers and FWL.  %% In particular, we
  %% have found that a two-stage verification engine that continuously refines
  %% the precision of the fixed-point representation of the plant yields a
  %% speed-up of two orders of magnitude over a conventional one-stage
  %% verification engine.
%
  %\item  We compute
  The computed state-feedback controllers 
  guarantee a given safety property alongside stability and safety
  specifications. Existing methods for controller synthesis rely on transfer
  function representations, which are inadequate to prove safety requirements.
%
\item We provide two novel algorithms: the first, na\"ive one, relies on
  an unfolding of the dynamics up to a completeness threshold, while the
  second one is abstraction-based and leverages abstraction refinement and
  acceleration to improve scalability while retaining soundness.  %% A third
  %% algorithm evaluates systems using transfer functions where no state-space
  %% description is given.
  Both approaches provide sound synthesis of
  feedback controllers and consider the various sources of imprecision in
  the implementation of the control algorithm and in the modeling of the
  plant.
%
\item We develop a model for different sources of quantization error and
  their effect on reachability properties.  We give bounds that ensure the
  safety of our controllers in a hybrid continuous-digital domain.

\item While \cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to systems
  modeled in discrete time, in the current paper we present a model for
  soundly evaluating reachability in a combined continuous-discrete time/space.
\item A further limitation of the work in \cite{DBLP:conf/cav/AbateBCCDKKP17}
  is its restriction to fixed-point arithmetic, meaning that fixed-point numbers
  were employed for the representation of both the plant and the controller, as well as for
  the operations performed by each of them.
  Conversely, in the current paper we also make use of floating-point arithmetic
  and compare the two approaches. Additionally, we enhance the implementation with an SMT backend, allowing us to also use reals in order to represent the states of the plant.
\end{enumerate}
